Modeling electrostatics in molecular biology: A tutorial of DelPhi and associated resources [Article v\versionnumber]

### 2019-11-12 article-manuscript/LiveCoMS_Article_ASAP_V1.tex
Changes to incorporate ASAP details

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,tutorial]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% Use the "ASAPversion' option following article acceptance to add the DOI and relevant dates to the document footer.
% Use the 'pubversion' option for adding the citation and publication information to the document footer, when the LiveCoMS issue is finalized.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

\usepackage{lipsum} % Required to insert dummy text
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\DeclareSIUnit\Molar{M}
\usepackage[italic]{mathastext}
\usepackage{hyperref}
\graphicspath{{figures/}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pubDOI{10.XXXX/YYYYYYY}
\pubvolume{<volume>}
\pubissue{<issue>}
\pubyear{<year>}
\articlenum{<number>}
\datereceived{Day Month Year}
\dateaccepted{Day Month Year}

@@

The third term represents the energy of interactions between permanent charges and mobile ions. Formally it could be described by a formula similar to Eqn. \ref{eqn:G_rxn}, where instead of induced charges one takes excess ion density. However, this approach was abandoned in the newest DelPhi version because it is very slow and requires small “percent fill”. Instead, we recommend using grid energy difference between runs with salt and without salt.

@@

\bibliography{manuscript-v01}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,tutorial,ASAPversion]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% Use the "ASAPversion' option following article acceptance to add the DOI and relevant dates to the document footer.
% Use the 'pubversion' option for adding the citation and publication information to the document footer, when the LiveCoMS issue is finalized.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

%\usepackage{lipsum} % Required to insert dummy text

\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\DeclareSIUnit\Molar{M}
\usepackage[italic]{mathastext}
\usepackage{hyperref}
\graphicspath{{figures/}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pubDOI{10.33011/livecoms.1.2.10841}
\pubvolume{1}
\pubissue{2}
\pubyear{2019}
\articlenum{10841}
\datereceived{25 June 2019}
\dateaccepted{27 October 2019}

@@

The third term represents the energy of interactions between permanent charges and mobile ions. Formally it could be described by a formula similar to Eqn. \ref{eqn:G_rxn}, where instead of induced charges one takes excess ion density. However, while this approach is still supported in the newest DelPhi version, it is very slow and requires small “percent fill”. Therefore, we recommend using grid energy difference between runs with and without salt instead.

@@

\section*{Author Information}
\makeorcid
\begin{tabular}{lcl}
	Shailesh Kumar Panday  &:& 0000-0003-3099-8679 \\
	Mihiri H.B. Shashikala &:& 0000-0001-7812-9902 \\
	Mahesh Koirala         &:& 0000-0001-5787-1972 \\
	Swagata Pahari         &:& 0000-0001-9192-9250 \\
	Arghya Chakrvorty      &:& 0000-0002-4467-1135 \\
	Yunhui Peng            &:& 0000-0001-9768-4127 \\
	Lin Li                 &:& 0000-0001-6447-2398 \\
	Zhe Jia                &:& 0000-0001-7709-9692 \\
	Chuan Li               &:& 0000-0003-2414-4781 \\
	Emil Alexov            &:& 0000-0001-5346-0156 \\
\end{tabular}

\bibliography{LiveCoMS_Article_V1}
